Governing through patronage: the bargain for education in decentralized Brazil

### 2020-11-09 paper/paper.tex
initiate descriptives for saeb_principal

@@

Brazil collects fine-grained data on education and makes it publicly available for research. For this study, data on education are collected from two main sources: the SAEB and School Census.\footnote{These can be accessed \hyperlink{http://portal.inep.gov.br/web/guest/dados}{here}.} The SAEB (National System for Educational Assessment) is a biannual standardized exam administered by the INEP (National Institute fosr Educational Studies and Research) to all public schools and a sample of private schools. In 2017, over 5 million students, in 5th and 9th grade, took the exam, testing their proficiency in both mathematics and Portuguese. In this study, test scores are the primary metric for assessing the quality of education received by students.

>>>>

Teachers and school principals are responsible for providing all educational services at the local level. As of 2016, in the municipal education system there were 3.7 million teachers distributed across the national territory, as well as 148 thousand school principals. TableA majority of teachers are hired with a permanent contract (\emph{estatutário}) Over the past decade, there has been an increasing

\begin{table}[h]
    \centering
    \footnotesize
    \input{results/turnover_result}
    \caption{{\bf Executive coalitions and staff turnover.} An increase in the share of legislative seats held by the mayoral coalition decrease the amount of turnover for teachers and school principals, including hires or dismissals. Models 1 and 2 present results on the turnover index at the school level. Models 2 and 3 are aggregate hiring rates at the municipal level. Models 5 and 6 are logistic regressions at the individual, bureaucrat level. where the outcome of interest is the proportion of staff either hired or dismissed at a given year. Models 1, 3, and 5 include year and state fixed effects.}
    \label{tbl:turnover}
  \end{table}

@@

Brazil collects fine-grained data on education and makes it publicly available for research. For this study, data on education are collected from two main sources: the SAEB and School Census.\footnote{These can be accessed \hyperlink{http://portal.inep.gov.br/web/guest/dados}{here}.} The SAEB (National System for Educational Assessment) is a biannual standardized exam administered by the INEP (National Institute for Educational Studies and Research) to all public schools and a sample of private schools. In 2017, over 5 million students, in 5th and 9th grade, took the exam, testing their proficiency in both mathematics and Portuguese. In this study, test scores are the primary metric for assessing the quality of education received by students.
